---
title: "analysis1"
author: "Nate Thomas"
date: "`r Sys.Date()`"
output: html_document
---

all data was downloaded from https://archive.cdc.gov/www_cdc_gov/nchs/nhis/1997-2018.htm

```{r setup, include=FALSE}
library(haven)
library(tidyverse)
library(epiR)
library(survey)
library(caret)
library(pROC)
library(broom)

year <- 2013:2017
for (yr in year){
  print(yr)
  if (!exists("personsx")){
    personsx <- haven::read_sas(paste0("../Data2 - Redo to clean it up/",yr,"/personsx/personsx.sas7bdat"))
    names(personsx) <- names(personsx) %>% str_to_upper()
  } else {
    tmp <- haven::read_sas(paste0("../Data2 - Redo to clean it up/",yr,"/personsx/personsx.sas7bdat"))
    names(tmp) <- names(tmp) %>% str_to_upper()
    personsx <- personsx %>%
      bind_rows(tmp)

  }
  if (!exists("familyxx")){
    familyxx <- haven::read_sas(paste0("../Data2 - Redo to clean it up/",yr,"/familyxx/familyxx.sas7bdat"))
    names(familyxx) <- names(familyxx) %>% str_to_upper()
  } else {
    tmp <- haven::read_sas(paste0("../Data2 - Redo to clean it up/",yr,"/familyxx/familyxx.sas7bdat"))
    names(tmp) <- names(tmp) %>% str_to_upper()
    familyxx <- familyxx %>%
      bind_rows(tmp)
  }
  if (!exists("funcdisb")){
    funcdisb <- haven::read_sas(paste0("../Data2 - Redo to clean it up/",yr,"/funcdisb/funcdisb.sas7bdat"))
    names(funcdisb) <- names(funcdisb) %>% str_to_upper()
  } else {
    tmp <- haven::read_sas(paste0("../Data2 - Redo to clean it up/",yr,"/funcdisb/funcdisb.sas7bdat"))
    names(tmp) <- names(tmp) %>% str_to_upper()
    funcdisb <- funcdisb %>%
      bind_rows(tmp)
  }

}
save.image(".RData")

load(".RData")
```

# Person File:

## Intellectual Disability
LAHCC7A: What conditions or health problems cause {person} limitations? 
  (PLAPLYLM ='1' or PSPEDEIS ='1' or PLAADL ='1' or PLAWALK='1' or PLAREMEM ='1' or PLIMANY ='1')
LAHCA14A: What conditions or health problems cause {person} limitations? 
  (PLAADL ='1' or PLAIADL ='1' or PLAWKNOW ='1' or PLAWKLIM ='1' or PLAWALK ='1' or PLAREMEM ='1' or PLIMANY ='1')

## Developmental Disability
LAHCC8: What conditions or health problems cause {person} limitations?
  (PLAPLYLM ='1' or PSPEDEIS ='1' or PLAADL ='1' or PLAWALK='1' or PLAREMEM ='1' or PLIMANY ='1')
LAHCA15: What conditions or health problems cause {person} limitations? 
  (PLAADL ='1' or PLAIADL ='1' or PLAWKNOW ='1' or PLAWKLIM ='1' or PLAWALK ='1' or PLAREMEM ='1' or PLIMANY ='1') 

## Limiation
PLAPLYLM: {Are/Is} (* Read names below) limited in the kind or amount of play activities {he/she/they} can do because of a
physical, mental, or emotional problem?
PSPEDEIS: Do any of the following family members, (* Read names below) receive Special Educational or Early Intervention
Services? 
PLAWALK: Because of a health problem, {do you/does anyone in the family} have difficulty walking without using any special
equipment? 
PLAREMEM: {Are you/Is anyone in the family} LIMITED IN ANY WAY because of difficulty remembering or because {you/they}
experience periods of confusion? 
PLIMANY: Are {you/any family members} LIMITED IN ANY WAY in any activities because of physical, mental or emotional
problems?

## ADL
PLAADL: Because of a physical, mental, or emotional problem, {do you/does anyone in the family} need the help of other persons
with PERSONAL CARE NEEDS, such as eating, bathing, dressing, or getting around inside this home? 

## IADL
PLAIADL: Because of a physical, mental, or emotional problem, do {you/any of these family members (* Read named below)}
need the help of other persons in handling ROUTINE NEEDS, such as everyday household chores, doing necessary
business, shopping, or getting around for other purposes? 

## PR
PLAWKNOW: Does a physical, mental, or emotional problem NOW keep {you/any of these family members} from working at a job or
business? 
PLAWKLIM: {Are you limited in the kind OR amount of work you/Are any of these family members limited in the kind OR amount
of work they} can do because of a physical, mental or emotional problem? 

## Education
EDUC: What is the HIGHEST level of school {person has} completed or the highest degree {person has} received? Please tell
me the number from the card. 

# Unweighted Obs

```{r}
# Intellectual Disability
#table(personsx$LAHCC7A, personsx$SRVY_YR) %>% sum()
#table(personsx$LAHCA14A, personsx$SRVY_YR) %>% sum()

# Developmental Disability
#table(personsx$LAHCC8, personsx$SRVY_YR)
#table(personsx$LAHCA15, personsx$SRVY_YR)

# Age
#table(personsx$AGE_P, personsx$SRVY_YR)

# PSU
#table(is.na(personsx$PSU_P))
# Strat
#table(is.na(personsx$STRAT_P))
```

```{r}
# Clean the data
personsx_clean <- personsx %>%
  filter(AGE_P >= 18 & AGE_P <= 64) %>%                                         # Set age group
  mutate(id_ = ifelse((LAHCC7A == 1) | (LAHCA14A == 1), 1, NA),                 # Init ID
         dd_ = ifelse((LAHCC8  == 1) | (LAHCA15  == 1), 1, NA)) %>%             # Init DD
  mutate(id_ = ifelse(is.na(id_), 0, id_),                                      # Fill NA
         dd_ = ifelse(is.na(dd_), 0, dd_),                                      # Fill NA
         idd_= ifelse(id_ | dd_, 1, 0),                                         # Set IDD
         PSU = ifelse(is.na(PSU_P), PPSU, PSU_P),                               # Variable name change for PSU
         STRAT = ifelse(is.na(STRAT_P), PSTRAT, STRAT_P),                       # Variable name change for Strata
         WTFA  = WTFA/7) %>%                                                    # Correct weights for pooled years
  mutate(id_f  = id_  %>% as.factor(),
         dd_f  = dd_  %>% as.factor(),
         idd_f = idd_ %>% as.factor())

sum(is.na(personsx_clean$STRAT))
```

```{r}
svydes <- survey::svydesign(ids = ~PSU,
                            data = personsx_clean,
                            strata = ~STRAT,
                            weights = ~WTFA,
                            nest = T)

id_prev <- svymean(~id_f, design = svydes)
id_pop  <- svytotal(~id_f, design = svydes)

dd_prev <- svymean(~dd_f, design = svydes)
dd_pop  <- svytotal(~dd_f, design = svydes)

idd_prev <- svymean(~idd_f, design = svydes)
idd_pop  <- svytotal(~idd_f, design = svydes)
```

# Functioning File:

## Intellectual Disability
N/A

## Developmental Disability
N/A

## Limiation
COG_SS: Do you have difficulty remembering or concentrating? Would you say no difficulty, some difficulty, a lot of difficulty, or
are you unable to do this?

## ADL
UB_SS: Do you have difficulty with self-care, such as washing all over or dressing? Would you say no difficulty, some difficulty,
a lot of difficulty, or are you unable to do this? 

## IADL
N/A - 

## EDUCATION
N/A

```{r}
combined_clean <- personsx_clean %>%
  left_join(funcdisb, by = c("HHX","FPX","FMX","SRVY_YR"))     

overlap <- combined_clean %>%
  select(contains(".x"),contains(".y"))

# check if tabled overlap variables perfectly agree
#table(overlap$RECTYPE.x,overlap$RECTYPE.y)
#table(overlap$INTV_QRT.x,overlap$INTV_QRT.y)
#table(overlap$INTV_MON.x,overlap$INTV_MON.y)
#isDiagonal(table(overlap$STRAT_P.x,overlap$STRAT_P.y) %>% matrix(ncol = 300))
#table(overlap$PSU_P.x,overlap$PSU_P.y)
#table(overlap$FDRN_FLG.x,overlap$FDRN_FLG.y)
#table(overlap$AFD_FLG.x,overlap$AFD_FLG.y)
#isDiagonal(table(overlap$PSTRAT.x,overlap$PSTRAT.y) %>% matrix(ncol = 52))
#table(overlap$PPSU.x,overlap$PPSU.y)

combined_clean <- personsx_clean %>%
  select(-WTFA) %>%
  left_join(funcdisb %>%
              select(-INTV_QRT,-INTV_MON,-STRAT_P,
                     -PSU_P,-FDRN_FLG,-PSTRAT,-PPSU,-AFD_FLG), 
            by = c("HHX","FPX","FMX","SRVY_YR")) %>%
  filter(RECTYPE.y == 38) %>%
  mutate(cog       = ifelse(COG_SS %in% c(2:4), 1, 0),                          #  Cognitive difficulty
         self  = ifelse(UB_SS %in% c(2:4) | PLAADL == 1,1,0),                   # ADL
         ind = ifelse(PLAIADL == 1, 1, 0),                                      # IADL
         lesshs    = ifelse(EDUC1 %in% c(0:12), 1, 0),                       # Less than a high school diploma | Don't know
         WTFA_AFD  = WTFA_AFD/7) %>%
  mutate(cog.self = ifelse(cog & self, 1, 0),
         cog.ind = ifelse(cog & ind, 1, 0),
         cog.self.ind = ifelse(cog & (self | ind), 1, 0),
         cog.self.ind.lesshs = ifelse(cog & (self | ind) & lesshs, 1, 0),
         cog.self.lesshs = ifelse(cog & self & lesshs, 1, 0),
         cog.ind.lesshs = ifelse(cog & ind & lesshs, 1, 0),
         ind.lesshs = ifelse(ind & lesshs, 1, 0),
         self.ind.lesshs = ifelse((self | ind) & lesshs, 1, 0)) %>%
  mutate(cog_f  = cog  %>% as.factor(),
         cog.self_f = cog.self %>% as.factor(),
         cog.ind_f = cog.ind %>% as.factor(),
         cog.self.ind_f  = cog.self.ind  %>% as.factor(),
         cog.self.ind.lesshs_f = cog.self.ind.lesshs %>% as.factor(),
         cog.self.lesshs_f = cog.self.lesshs %>% as.factor(),
         cog.ind.lesshs_f = cog.ind.lesshs %>% as.factor(),
         ind.lesshs_f = ind.lesshs %>% as.factor(),
         self.ind.lesshs_f = self.ind.lesshs %>% as.factor(),
         allones = 1,
         id_cog = paste0(id_,cog),
         id_self = paste0(id_,self),
         id_ind = paste0(id_,ind),
         id_cog.self = paste0(id_,cog.self),
         id_cog.ind = paste0(id_,cog.ind),
         id_cog.self.ind = paste0(id_,cog.self.ind),
         id_cog.self.ind.lesshs = paste0(id_,cog.self.ind.lesshs),
         id_cog.self.lesshs = paste0(id_,cog.self.lesshs),
         id_cog.ind.lesshs = paste0(id_,cog.ind.lesshs),
         id_ind.lesshs = paste0(id_,ind.lesshs),
         id_self.ind.lesshs = paste0(id_,self.ind.lesshs),
         dd_cog = paste0(dd_,cog),
         dd_self = paste0(dd_,self),
         dd_ind = paste0(dd_,ind),
         dd_cog.self = paste0(dd_,cog.self),
         dd_cog.ind = paste0(dd_,cog.ind),
         dd_cog.self.ind = paste0(dd_,cog.self.ind),
         dd_cog.self.ind.lesshs = paste0(dd_,cog.self.ind.lesshs),
         dd_cog.self.lesshs = paste0(dd_,cog.self.lesshs),
         dd_cog.ind.lesshs = paste0(dd_,cog.ind.lesshs),
         dd_ind.lesshs = paste0(dd_,ind.lesshs),
         dd_self.ind.lesshs = paste0(dd_,self.ind.lesshs),
         idd_cog = paste0(idd_,cog),
         idd_self = paste0(idd_,self),
         idd_ind = paste0(idd_,ind),
         idd_cog.self = paste0(idd_,cog.self),
         idd_cog.ind = paste0(idd_,cog.ind),
         idd_cog.self.ind = paste0(idd_,cog.self.ind),
         idd_cog.self.ind.lesshs = paste0(idd_,cog.self.ind.lesshs),
         idd_cog.self.lesshs = paste0(idd_,cog.self.lesshs),
         idd_cog.ind.lesshs = paste0(idd_,cog.ind.lesshs),
         idd_ind.lesshs = paste0(idd_,ind.lesshs),
         idd_self.ind.lesshs = paste0(idd_,self.ind.lesshs))

#table(is.na(combined_clean$ind))
#table(combined_clean$RECTYPE.y, combined_clean$SRVY_YR)
#table(combined_clean$RECTYPE.x, combined_clean$SRVY_YR)
#table(combined_clean$cog, combined_clean$SRVY_YR)
#table(combined_clean$self, combined_clean$SRVY_YR)
#table(combined_clean$ind, combined_clean$SRVY_YR)
#table(combined_clean$lesshs, combined_clean$SRVY_YR)
```

```{r}
svydes_proxy <- survey::svydesign(ids = ~PSU,
                            data = combined_clean,
                            strata = ~STRAT,
                            weights = ~WTFA_AFD,
                            nest = T)

id_prop <- svymean(~as.factor(id_), design = svydes_proxy)
dd_prop <- svymean(~as.factor(dd_), design = svydes_proxy)
idd_prop <- svymean(~as.factor(idd_), design = svydes_proxy)

cog_prev <- svymean(~cog_f, design = svydes_proxy)
cog_pop  <- svytotal(~cog_f, design = svydes_proxy)

cog.self_prev <- svymean(~cog.self_f, design = svydes_proxy)
cog.self_pop  <- svytotal(~cog.self_f, design = svydes_proxy)

cog.ind_prev <- svymean(~cog.ind_f, design = svydes_proxy)
cog.ind_pop  <- svytotal(~cog.ind_f, design = svydes_proxy)

cog.self.ind_prev <- svymean(~cog.self.ind_f, design = svydes_proxy)
cog.self.ind_pop  <- svytotal(~cog.self.ind_f, design = svydes_proxy)

cog.self.ind.lesshs_prev <- svymean(~cog.self.ind.lesshs_f, design = svydes_proxy)
cog.self.ind.lesshs_pop  <- svytotal(~cog.self.ind.lesshs_f, design = svydes_proxy)
```

## ID Pop and Prevalence 

```{r}
id_cog_pop  <- svytotal(~id_cog, design = svydes_proxy)
id_cog_prev <- svymean(~id_cog, design = svydes_proxy)

table(combined_clean$dd_, combined_clean$self)
id_self_pop  <- svytotal(~id_self, design = svydes_proxy)
id_self_prev <- svymean(~id_self, design = svydes_proxy)

table(combined_clean$dd_, combined_clean$ind)
id_ind_pop  <- svytotal(~id_ind, design = svydes_proxy)
id_ind_prev <- svymean(~id_ind, design = svydes_proxy)

id_cog.self_pop  <- svytotal(~id_cog.self, design = svydes_proxy)
id_cog.self_prev <- svymean(~id_cog.self, design = svydes_proxy)

id_cog.ind_pop  <- svytotal(~id_cog.ind, design = svydes_proxy)
id_cog.ind_prev <- svymean(~id_cog.ind, design = svydes_proxy)

id_cog.self.ind_pop  <- svytotal(~id_cog.self.ind, design = svydes_proxy)
id_cog.self.ind_prev <- svymean(~id_cog.self.ind, design = svydes_proxy)

id_cog.self.ind.lesshs_pop  <- svytotal(~id_cog.self.ind.lesshs, design = svydes_proxy)
id_cog.self.ind.lesshs_prev <- svymean(~id_cog.self.ind.lesshs, design = svydes_proxy)

id_cog.ind.lesshs_pop  <- svytotal(~id_cog.ind.lesshs, design = svydes_proxy)
id_cog.ind.lesshs_prev <- svymean(~id_cog.ind.lesshs, design = svydes_proxy)
table(combined_clean$id_, combined_clean$cog.ind.lesshs) 

id_cog.self.lesshs_pop  <- svytotal(~id_cog.self.lesshs, design = svydes_proxy)
id_cog.self.lesshs_prev <- svymean(~id_cog.self.lesshs, design = svydes_proxy)
table(combined_clean$id_, combined_clean$cog.self.lesshs) 

id_ind.lesshs_pop  <- svytotal(~id_ind.lesshs, design = svydes_proxy)
id_ind.lesshs_prev <- svymean(~id_ind.lesshs, design = svydes_proxy)
table(combined_clean$id_, combined_clean$ind.lesshs) 

id_self.ind.lesshs_pop  <- svytotal(~id_self.ind.lesshs, design = svydes_proxy)
id_self.ind.lesshs_prev <- svymean(~id_self.ind.lesshs, design = svydes_proxy)
table(combined_clean$id_, combined_clean$self.ind.lesshs) 
```

## DD Pop and Prevalence 

```{r}
table(combined_clean$dd_, combined_clean$cog)
dd_cog_pop  <- svytotal(~dd_cog, design = svydes_proxy)
dd_cog_prev <- svymean(~dd_cog, design = svydes_proxy)

table(combined_clean$dd_, combined_clean$cog.self)
dd_cog.self_pop  <- svytotal(~dd_cog.self, design = svydes_proxy)
dd_cog.self_prev <- svymean(~dd_cog.self, design = svydes_proxy)

table(combined_clean$dd_, combined_clean$cog.ind)
dd_cog.ind_pop  <- svytotal(~dd_cog.ind, design = svydes_proxy)
dd_cog.ind_prev <- svymean(~dd_cog.ind, design = svydes_proxy)

table(combined_clean$dd_, combined_clean$cog.self.ind)
dd_cog.self.ind_pop  <- svytotal(~dd_cog.self.ind, design = svydes_proxy)
dd_cog.self.ind_prev <- svymean(~dd_cog.self.ind, design = svydes_proxy)

table(combined_clean$dd_, combined_clean$cog.self.ind.lesshs)
dd_cog.self.ind.lesshs_pop  <- svytotal(~dd_cog.self.ind.lesshs, design = svydes_proxy)
dd_cog.self.ind.lesshs_prev <- svymean(~dd_cog.self.ind.lesshs, design = svydes_proxy)

table(combined_clean$dd_, combined_clean$cog.ind.lesshs) 
dd_cog.ind.lesshs_pop  <- svytotal(~dd_cog.ind.lesshs, design = svydes_proxy)
dd_cog.ind.lesshs_prev <- svymean(~dd_cog.ind.lesshs, design = svydes_proxy)

table(combined_clean$dd_, combined_clean$cog.self.lesshs) 
dd_cog.self.lesshs_pop  <- svytotal(~dd_cog.self.lesshs, design = svydes_proxy)
dd_cog.self.lesshs_prev <- svymean(~dd_cog.self.lesshs, design = svydes_proxy)

table(combined_clean$dd_, combined_clean$ind.lesshs) 
dd_ind.lesshs_pop  <- svytotal(~dd_ind.lesshs, design = svydes_proxy)
dd_ind.lesshs_prev <- svymean(~dd_ind.lesshs, design = svydes_proxy)

table(combined_clean$dd_, combined_clean$self.ind.lesshs) 
dd_self.ind.lesshs_pop  <- svytotal(~dd_self.ind.lesshs, design = svydes_proxy)
dd_self.ind.lesshs_prev <- svymean(~dd_self.ind.lesshs, design = svydes_proxy)
```

## IDD Pop and Prevalence 

```{r}
table(combined_clean$idd_, combined_clean$cog)
idd_cog_pop  <- svytotal(~idd_cog, design = svydes_proxy)
idd_cog_prev <- svymean(~idd_cog, design = svydes_proxy)

table(combined_clean$idd_, combined_clean$cog.self)
idd_cog.self_pop  <- svytotal(~idd_cog.self, design = svydes_proxy)
idd_cog.self_prev <- svymean(~idd_cog.self, design = svydes_proxy)

table(combined_clean$idd_, combined_clean$cog.ind)
idd_cog.ind_pop  <- svytotal(~idd_cog.ind, design = svydes_proxy)
idd_cog.ind_prev <- svymean(~idd_cog.ind, design = svydes_proxy)

table(combined_clean$idd_, combined_clean$cog.self.ind)
idd_cog.self.ind_pop  <- svytotal(~idd_cog.self.ind, design = svydes_proxy)
idd_cog.self.ind_prev <- svymean(~idd_cog.self.ind, design = svydes_proxy)

table(combined_clean$idd_, combined_clean$cog.self.ind.lesshs)
idd_cog.self.ind.lesshs_pop  <- svytotal(~idd_cog.self.ind.lesshs, design = svydes_proxy)
idd_cog.self.ind.lesshs_prev <- svymean(~idd_cog.self.ind.lesshs, design = svydes_proxy)

table(combined_clean$idd_, combined_clean$cog.ind.lesshs) 
idd_cog.ind.lesshs_pop  <- svytotal(~idd_cog.ind.lesshs, design = svydes_proxy)
idd_cog.ind.lesshs_prev <- svymean(~idd_cog.ind.lesshs, design = svydes_proxy)

table(combined_clean$idd_, combined_clean$cog.self.lesshs) 
idd_cog.self.lesshs_pop  <- svytotal(~idd_cog.self.lesshs, design = svydes_proxy)
idd_cog.self.lesshs_prev <- svymean(~idd_cog.self.lesshs, design = svydes_proxy)

table(combined_clean$idd_, combined_clean$ind.lesshs) 
idd_ind.lesshs_pop  <- svytotal(~idd_ind.lesshs, design = svydes_proxy)
idd_ind.lesshs_prev <- svymean(~idd_ind.lesshs, design = svydes_proxy)

table(combined_clean$idd_, combined_clean$self.ind.lesshs) 
idd_self.ind.lesshs_pop  <- svytotal(~idd_self.ind.lesshs, design = svydes_proxy)
idd_self.ind.lesshs_prev <- svymean(~idd_self.ind.lesshs, design = svydes_proxy)
```


# Kappa Agreement

## Source: 
https://search.r-project.org/CRAN/refmans/epiR/html/epi.kappa.html
"
Kappa is a measure of agreement beyond the level of agreement expected by chance alone. The observed agreement is the proportion of samples for which both methods (or observers) agree.

The bias and prevalence adjusted kappa (Byrt et al. 1993) provides a measure of observed agreement, an index of the bias between observers, and an index of the differences between the overall proportion of ‘yes’ and ‘no’ assessments. Bias and prevalence adjusted kappa are only returned if the number of rows and columns of argument dat equal 2.

Common interpretations for the kappa statistic are as follows: < 0.2 slight agreement, 0.2 - 0.4 fair agreement, 0.4 - 0.6 moderate agreement, 0.6 - 0.8 substantial agreement, > 0.8 almost perfect agreement (Sim and Wright, 2005).

Confidence intervals for the proportion of observations where there is agreement are calculated using the exact method (Collett 1999).

The argument alternative = "greater" tests the hypothesis that kappa is greater than 0.
"

## Source: 
https://www.sciencedirect.com/science/article/pii/S0895435699001742#:~:text=The%20first%20paradox%20is%20shown,two%20observers%20in%20marginal%20proportions.

"PABAK adjusts for these factors by assuming a 50% prevalence and no bias, which can lead to a higher kappa value. The standard kappa statistic can be misleading when prevalence is low or there is significant bias, as these factors can artificially decrease the kappa value. "

"
If the prevalence of a condition in the sample is very high or low, the kappa statistic can be artificially lowered, even if there is good agreement between raters. This is because the kappa statistic considers the amount of agreement expected by chance, and chance agreement is higher when prevalence is extreme. 
"

## ID and Cog, prev. and bias adjusted kappa

```{r}
id.x.cog <- table(combined_clean$id_, combined_clean$cog) %>% matrix(nrow = 2) 
id.x.cog <- matrix(c(id.x.cog[2,2],id.x.cog[1,2],id.x.cog[2,1],id.x.cog[1,1]), nrow =2)

id.x.cog.kappa <- epi.kappa(dat = id.x.cog, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
id.x.cog.kappa$pabak # the prevalence and bias corrected kappa statistic and the lower and upper bounds of the confidence interval for the prevalence and bias corrected kappa statistic
id.x.cog.kappa$kappa # the kappa statistic, the standard error of the kappa statistic and the lower and upper bounds of the confidence interval for the kappa statistic.
```

```{r}
id.x.cog[1,1]*id.x.cog[2,2]/(id.x.cog[1,2]*id.x.cog[2,1])
confusionMatrix(id.x.cog)
```

```{r}
id.x.cog_wt <- matrix(round(c(id_cog_pop[4],id_cog_pop[2],id_cog_pop[3],id_cog_pop[1])), nrow = 2)

id.x.cog_wt.kappa <- epi.kappa(dat = id.x.cog_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
id.x.cog_wt.kappa$pabak # the prevalence and bias corrected kappa statistic and the lower and upper bounds of the confidence interval for the prevalence and bias corrected kappa statistic
id.x.cog_wt.kappa$kappa # the kappa statistic, the standard error of the kappa statistic and the lower and upper bounds of the confidence interval for the kappa statistic.
```

```{r}
id.x.cog_wt[1,1]*id.x.cog_wt[2,2]/(id.x.cog_wt[1,2]*id.x.cog_wt[2,1])
confusionMatrix(id.x.cog_wt)
```

## ID and Cog & Selfcare , prev. and bias adjusted kappa

```{r}
id.x.cog.self <- table(combined_clean$id_, combined_clean$cog.self) %>% matrix(nrow = 2) 
id.x.cog.self <- matrix(c(id.x.cog.self[2,2],id.x.cog.self[1,2],id.x.cog.self[2,1],id.x.cog.self[1,1]), nrow =2)

id.x.cog.self.kappa <- epi.kappa(dat = id.x.cog.self, method = "fleiss", alternative = "two.sided", conf.level = 0.95)

id.x.cog.self.kappa$kappa
id.x.cog.self.kappa$pabak 
```

```{r}
id.x.cog.self[1,1]*id.x.cog.self[2,2]/(id.x.cog.self[1,2]*id.x.cog.self[2,1])
confusionMatrix(id.x.cog.self)
```

```{r}
id.x.cog.self_wt <- matrix(round(c(id_cog.self_pop[4],id_cog.self_pop[2],id_cog.self_pop[3],id_cog.self_pop[1])), nrow = 2)

id.x.cog.self_wt.kappa <- epi.kappa(dat = id.x.cog.self_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
id.x.cog.self_wt.kappa$pabak 
id.x.cog.self_wt.kappa$kappa 
```

```{r}
id.x.cog.self_wt[1,1]*id.x.cog.self_wt[2,2]/(id.x.cog.self_wt[1,2]*id.x.cog.self_wt[2,1])
confusionMatrix(id.x.cog.self_wt)
```

## ID and Cog & Independent Living , prev. and bias adjusted kappa

```{r}
id.x.cog.ind <- table(combined_clean$id_, combined_clean$cog.ind) %>% matrix(nrow = 2) 
id.x.cog.ind <- matrix(c(id.x.cog.ind[2,2],id.x.cog.ind[1,2],id.x.cog.ind[2,1],id.x.cog.ind[1,1]), nrow =2)

id.x.cog.ind.kappa <- epi.kappa(dat = id.x.cog.ind, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
id.x.cog.ind.kappa$pabak 
id.x.cog.ind.kappa$kappa
```

```{r}
id.x.cog.ind[1,1]*id.x.cog.ind[2,2]/(id.x.cog.ind[1,2]*id.x.cog.ind[2,1])
confusionMatrix(id.x.cog.ind)
```

```{r}
id.x.cog.ind_wt <- matrix(round(c(id_cog.ind_pop[4],id_cog.ind_pop[2],id_cog.ind_pop[3],id_cog.ind_pop[1])), nrow = 2)

id.x.cog.ind_wt.kappa <- epi.kappa(dat = id.x.cog.ind_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
id.x.cog.ind_wt.kappa$pabak 
id.x.cog.ind_wt.kappa$kappa 
```

```{r}
id.x.cog.ind_wt[1,1]*id.x.cog.ind_wt[2,2]/(id.x.cog.ind_wt[1,2]*id.x.cog.ind_wt[2,1])
confusionMatrix(id.x.cog.ind_wt)
```

## ID and Cog & (Selfcare | Independent Living) , prev. and bias adjusted kappa

```{r}
id.x.cog.self.ind <- table(combined_clean$id_, combined_clean$cog.self.ind) %>% matrix(nrow = 2) 
id.x.cog.self.ind <- matrix(c(id.x.cog.self.ind[2,2],id.x.cog.self.ind[1,2],id.x.cog.self.ind[2,1],id.x.cog.self.ind[1,1]), nrow =2)

id.x.cog.self.ind.kappa <- epi.kappa(dat = id.x.cog.self.ind, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
id.x.cog.self.ind.kappa$pabak 
id.x.cog.self.ind.kappa$kappa
```

```{r}
id.x.cog.self.ind[1,1]*id.x.cog.self.ind[2,2]/(id.x.cog.self.ind[1,2]*id.x.cog.self.ind[2,1])
confusionMatrix(id.x.cog.self.ind)
```

```{r}
id.x.cog.self.ind_wt <- matrix(round(c(id_cog.self.ind_pop[4],id_cog.self.ind_pop[2],id_cog.self.ind_pop[3],id_cog.self.ind_pop[1])), nrow = 2)

id.x.cog.self.ind_wt.kappa <- epi.kappa(dat = id.x.cog.self.ind_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
id.x.cog.self.ind_wt.kappa$pabak 
id.x.cog.self.ind_wt.kappa$kappa 
```

```{r}
id.x.cog.self.ind_wt[1,1]*id.x.cog.self.ind_wt[2,2]/(id.x.cog.self.ind_wt[1,2]*id.x.cog.self.ind_wt[2,1])
confusionMatrix(id.x.cog.self.ind_wt)
```

## ID and Cog & (Selfcare | Independent Living) & Less than HS , prev. and bias adjusted kappa

```{r}
id.x.cog.self.ind.lesshs <- table(combined_clean$id_, combined_clean$cog.self.ind.lesshs) %>% matrix(nrow = 2) 
id.x.cog.self.ind.lesshs <- matrix(c(id.x.cog.self.ind.lesshs[2,2],id.x.cog.self.ind.lesshs[1,2],id.x.cog.self.ind.lesshs[2,1],id.x.cog.self.ind.lesshs[1,1]), nrow =2)

id.x.cog.self.ind.lesshs.kappa <- epi.kappa(dat = id.x.cog.self.ind.lesshs, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
id.x.cog.self.ind.lesshs.kappa$pabak 
id.x.cog.self.ind.lesshs.kappa$kappa
```

```{r}
id.x.cog.self.ind.lesshs[1,1]*id.x.cog.self.ind.lesshs[2,2]/(id.x.cog.self.ind.lesshs[1,2]*id.x.cog.self.ind.lesshs[2,1])
confusionMatrix(id.x.cog.self.ind.lesshs)
```

```{r}
id.x.cog.self.ind.lesshs_wt <- matrix(round(c(id_cog.self.ind.lesshs_pop[4],id_cog.self.ind.lesshs_pop[2],id_cog.self.ind.lesshs_pop[3],id_cog.self.ind.lesshs_pop[1])), nrow = 2)

id.x.cog.self.ind.lesshs_wt.kappa <- epi.kappa(dat = id.x.cog.self.ind.lesshs_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
id.x.cog.self.ind.lesshs_wt.kappa$pabak 
id.x.cog.self.ind.lesshs_wt.kappa$kappa 
```

```{r}
id.x.cog.self.ind.lesshs_wt[1,1]*id.x.cog.self.ind.lesshs_wt[2,2]/(id.x.cog.self.ind.lesshs_wt[1,2]*id.x.cog.self.ind.lesshs_wt[2,1])
confusionMatrix(id.x.cog.self.ind.lesshs_wt)
```

## ID and Cog & Independent Living & Less than HS , prev. and bias adjusted kappa

```{r}
id.x.cog.ind.lesshs <- table(combined_clean$id_, combined_clean$cog.ind.lesshs) %>% matrix(nrow = 2) 
id.x.cog.ind.lesshs <- matrix(c(id.x.cog.ind.lesshs[2,2],id.x.cog.ind.lesshs[1,2],id.x.cog.ind.lesshs[2,1],id.x.cog.ind.lesshs[1,1]), nrow =2)

id.x.cog.ind.lesshs.kappa <- epi.kappa(dat = id.x.cog.ind.lesshs, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
id.x.cog.ind.lesshs.kappa$pabak 
id.x.cog.ind.lesshs.kappa$kappa
```

```{r}
id.x.cog.ind.lesshs[1,1]*id.x.cog.ind.lesshs[2,2]/(id.x.cog.ind.lesshs[1,2]*id.x.cog.ind.lesshs[2,1])
confusionMatrix(id.x.cog.ind.lesshs)
```

```{r}
id.x.cog.ind.lesshs_wt <- matrix(round(c(id_cog.ind.lesshs_pop[4],id_cog.ind.lesshs_pop[2],id_cog.ind.lesshs_pop[3],id_cog.ind.lesshs_pop[1])), nrow = 2)

id.x.cog.ind.lesshs_wt.kappa <- epi.kappa(dat = id.x.cog.ind.lesshs_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
id.x.cog.ind.lesshs_wt.kappa$pabak 
id.x.cog.ind.lesshs_wt.kappa$kappa 
```

```{r}
id.x.cog.ind.lesshs_wt[1,1]*id.x.cog.ind.lesshs_wt[2,2]/(id.x.cog.ind.lesshs_wt[1,2]*id.x.cog.ind.lesshs_wt[2,1])
confusionMatrix(id.x.cog.ind.lesshs_wt)
```

## ID and Cog & Self-care & Less than HS , prev. and bias adjusted kappa

```{r}
id.x.cog.self.lesshs <- table(combined_clean$id_, combined_clean$cog.self.lesshs) %>% matrix(nrow = 2) 
id.x.cog.self.lesshs <- matrix(c(id.x.cog.self.lesshs[2,2],id.x.cog.self.lesshs[1,2],id.x.cog.self.lesshs[2,1],id.x.cog.self.lesshs[1,1]), nrow =2)

id.x.cog.self.lesshs.kappa <- epi.kappa(dat = id.x.cog.self.lesshs, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
id.x.cog.self.lesshs.kappa$pabak 
id.x.cog.self.lesshs.kappa$kappa
```

```{r}
id.x.cog.self.lesshs[1,1]*id.x.cog.self.lesshs[2,2]/(id.x.cog.self.lesshs[1,2]*id.x.cog.self.lesshs[2,1])
confusionMatrix(id.x.cog.self.lesshs)
```

```{r}
id.x.cog.self.lesshs_wt <- matrix(round(c(id_cog.self.lesshs_pop[4],id_cog.self.lesshs_pop[2],id_cog.self.lesshs_pop[3],id_cog.self.lesshs_pop[1])), nrow = 2)

id.x.cog.self.lesshs_wt.kappa <- epi.kappa(dat = id.x.cog.self.lesshs_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
id.x.cog.self.lesshs_wt.kappa$pabak 
id.x.cog.self.lesshs_wt.kappa$kappa 
```

```{r}
id.x.cog.self.lesshs_wt[1,1]*id.x.cog.self.lesshs_wt[2,2]/(id.x.cog.self.lesshs_wt[1,2]*id.x.cog.self.lesshs_wt[2,1])
confusionMatrix(id.x.cog.self.lesshs_wt)
```


## ID and Independent Living & Less than HS , prev. and bias adjusted kappa

```{r}
id.x.ind.lesshs <- table(combined_clean$id_, combined_clean$ind.lesshs) %>% matrix(nrow = 2) 
id.x.ind.lesshs <- matrix(c(id.x.ind.lesshs[2,2],id.x.ind.lesshs[1,2],id.x.ind.lesshs[2,1],id.x.ind.lesshs[1,1]), nrow =2)

id.x.ind.lesshs.kappa <- epi.kappa(dat = id.x.ind.lesshs, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
id.x.ind.lesshs.kappa$pabak 
id.x.ind.lesshs.kappa$kappa
```

```{r}
id.x.ind.lesshs[1,1]*id.x.ind.lesshs[2,2]/(id.x.ind.lesshs[1,2]*id.x.ind.lesshs[2,1])
confusionMatrix(id.x.ind.lesshs)
```

```{r}
id.x.ind.lesshs_wt <- matrix(round(c(id_ind.lesshs_pop[4],id_ind.lesshs_pop[2],id_ind.lesshs_pop[3],id_ind.lesshs_pop[1])), nrow = 2)

id.x.ind.lesshs_wt.kappa <- epi.kappa(dat = id.x.ind.lesshs_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
id.x.ind.lesshs_wt.kappa$pabak 
id.x.ind.lesshs_wt.kappa$kappa 
```

```{r}
id.x.ind.lesshs_wt[1,1]*id.x.ind.lesshs_wt[2,2]/(id.x.ind.lesshs_wt[1,2]*id.x.ind.lesshs_wt[2,1])
confusionMatrix(id.x.ind.lesshs_wt)
```

## ID and Self-care | Independent Living & Less than HS , prev. and bias adjusted kappa

```{r}
id.x.self.ind.lesshs <- table(combined_clean$id_, combined_clean$self.ind.lesshs) %>% matrix(nrow = 2) 
id.x.self.ind.lesshs <- matrix(c(id.x.self.ind.lesshs[2,2],id.x.self.ind.lesshs[1,2],id.x.self.ind.lesshs[2,1],id.x.self.ind.lesshs[1,1]), nrow =2)

id.x.self.ind.lesshs.kappa <- epi.kappa(dat = id.x.self.ind.lesshs, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
id.x.self.ind.lesshs.kappa$pabak 
id.x.self.ind.lesshs.kappa$kappa
```

```{r}
id.x.self.ind.lesshs[1,1]*id.x.self.ind.lesshs[2,2]/(id.x.self.ind.lesshs[1,2]*id.x.self.ind.lesshs[2,1])
confusionMatrix(id.x.self.ind.lesshs)
```

```{r}
id.x.self.ind.lesshs_wt <- matrix(round(c(id_self.ind.lesshs_pop[4],id_self.ind.lesshs_pop[2],id_self.ind.lesshs_pop[3],id_self.ind.lesshs_pop[1])), nrow = 2)

id.x.self.ind.lesshs_wt.kappa <- epi.kappa(dat = id.x.self.ind.lesshs_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
id.x.self.ind.lesshs_wt.kappa$pabak 
id.x.self.ind.lesshs_wt.kappa$kappa 
```

```{r}
id.x.self.ind.lesshs_wt[1,1]*id.x.self.ind.lesshs_wt[2,2]/(id.x.self.ind.lesshs_wt[1,2]*id.x.self.ind.lesshs_wt[2,1])
confusionMatrix(id.x.self.ind.lesshs_wt)
```

#############################################################
#############################################################

## DD and Cog, prev. and bias adjusted kappa

```{r}
dd.x.cog <- table(combined_clean$dd_, combined_clean$cog) %>% matrix(nrow = 2) 
dd.x.cog <- matrix(c(dd.x.cog[2,2],dd.x.cog[1,2],dd.x.cog[2,1],dd.x.cog[1,1]), nrow =2)

dd.x.cog.kappa <- epi.kappa(dat = dd.x.cog, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
dd.x.cog.kappa$pabak 
dd.x.cog.kappa$kappa 
```

```{r}
dd.x.cog[1,1]*dd.x.cog[2,2]/(dd.x.cog[1,2]*dd.x.cog[2,1])
confusionMatrix(dd.x.cog)
```

```{r}
dd.x.cog_wt <- matrix(round(c(dd_cog_pop[4],dd_cog_pop[2],dd_cog_pop[3],dd_cog_pop[1])), nrow = 2)

dd.x.cog_wt.kappa <- epi.kappa(dat = dd.x.cog_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
dd.x.cog_wt.kappa$pabak 
dd.x.cog_wt.kappa$kappa 
```

```{r}
dd.x.cog_wt[1,1]*dd.x.cog_wt[2,2]/(dd.x.cog_wt[1,2]*dd.x.cog_wt[2,1])
confusionMatrix(dd.x.cog_wt)
```

## DD and Cog & Self-care, prev. and bias adjusted kappa

```{r}
dd.x.cog.self <- table(combined_clean$dd_, combined_clean$cog.self) %>% matrix(nrow = 2) 
dd.x.cog.self <- matrix(c(dd.x.cog.self[2,2],dd.x.cog.self[1,2],dd.x.cog.self[2,1],dd.x.cog.self[1,1]), nrow =2)

dd.x.cog.self.kappa <- epi.kappa(dat = dd.x.cog.self, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
dd.x.cog.self.kappa$pabak 
dd.x.cog.self.kappa$kappa 
```

```{r}
dd.x.cog.self[1,1]*dd.x.cog.self[2,2]/(dd.x.cog.self[1,2]*dd.x.cog.self[2,1])
confusionMatrix(dd.x.cog.self)
```

```{r}
dd.x.cog.self_wt <- matrix(round(c(dd_cog.self_pop[4],dd_cog.self_pop[2],dd_cog.self_pop[3],dd_cog.self_pop[1])), nrow = 2)

dd.x.cog.self_wt.kappa <- epi.kappa(dat = dd.x.cog.self_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
dd.x.cog.self_wt.kappa$pabak 
dd.x.cog.self_wt.kappa$kappa 
```

```{r}
dd.x.cog.self_wt[1,1]*dd.x.cog.self_wt[2,2]/(dd.x.cog.self_wt[1,2]*dd.x.cog.self_wt[2,1])
confusionMatrix(dd.x.cog.self_wt)
```

## DD and Cog & Independence Living, prev. and bias adjusted kappa

```{r}
dd.x.cog.ind <- table(combined_clean$dd_, combined_clean$cog.ind) %>% matrix(nrow = 2) 
dd.x.cog.ind <- matrix(c(dd.x.cog.ind[2,2],dd.x.cog.ind[1,2],dd.x.cog.ind[2,1],dd.x.cog.ind[1,1]), nrow =2)

dd.x.cog.ind.kappa <- epi.kappa(dat = dd.x.cog.ind, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
dd.x.cog.ind.kappa$pabak 
dd.x.cog.ind.kappa$kappa 
```

```{r}
dd.x.cog.ind[1,1]*dd.x.cog.ind[2,2]/(dd.x.cog.ind[1,2]*dd.x.cog.ind[2,1])
confusionMatrix(dd.x.cog.ind)
```

```{r}
dd.x.cog.ind_wt <- matrix(round(c(dd_cog.ind_pop[4],dd_cog.ind_pop[2],dd_cog.ind_pop[3],dd_cog.ind_pop[1])), nrow = 2)

dd.x.cog.ind_wt.kappa <- epi.kappa(dat = dd.x.cog.ind_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
dd.x.cog.ind_wt.kappa$pabak 
dd.x.cog.ind_wt.kappa$kappa 
```

```{r}
dd.x.cog.ind_wt[1,1]*dd.x.cog.ind_wt[2,2]/(dd.x.cog.ind_wt[1,2]*dd.x.cog.ind_wt[2,1])
confusionMatrix(dd.x.cog.ind_wt)
```

## DD and Cog & (Self-care  | Independence Living), prev. and bias adjusted kappa

```{r}
dd.x.cog.self.ind <- table(combined_clean$dd_, combined_clean$cog.self.ind) %>% matrix(nrow = 2) 
dd.x.cog.self.ind <- matrix(c(dd.x.cog.self.ind[2,2],dd.x.cog.self.ind[1,2],dd.x.cog.self.ind[2,1],dd.x.cog.self.ind[1,1]), nrow =2)

dd.x.cog.self.ind.kappa <- epi.kappa(dat = dd.x.cog.self.ind, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
dd.x.cog.self.ind.kappa$pabak 
dd.x.cog.self.ind.kappa$kappa 
```

```{r}
dd.x.cog.self.ind[1,1]*dd.x.cog.self.ind[2,2]/(dd.x.cog.self.ind[1,2]*dd.x.cog.self.ind[2,1])
confusionMatrix(dd.x.cog.self.ind)
```

```{r}
dd.x.cog.self.ind_wt <- matrix(round(c(dd_cog.self.ind_pop[4],dd_cog.self.ind_pop[2],dd_cog.self.ind_pop[3],dd_cog.self.ind_pop[1])), nrow = 2)

dd.x.cog.self.ind_wt.kappa <- epi.kappa(dat = dd.x.cog.self.ind_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
dd.x.cog.self.ind_wt.kappa$pabak 
dd.x.cog.self.ind_wt.kappa$kappa 
```

```{r}
dd.x.cog.self.ind_wt[1,1]*dd.x.cog.self.ind_wt[2,2]/(dd.x.cog.self.ind_wt[1,2]*dd.x.cog.self.ind_wt[2,1])
confusionMatrix(dd.x.cog.self.ind_wt)
```

## DD and Cog & (Self-care  | Independence Living) & Less than HS, prev. and bias adjusted kappa

```{r}
dd.x.cog.self.ind.lesshs <- table(combined_clean$dd_, combined_clean$cog.self.ind.lesshs) %>% matrix(nrow = 2) 
dd.x.cog.self.ind.lesshs <- matrix(c(dd.x.cog.self.ind.lesshs[2,2],dd.x.cog.self.ind.lesshs[1,2],dd.x.cog.self.ind.lesshs[2,1],dd.x.cog.self.ind.lesshs[1,1]), nrow =2)

dd.x.cog.self.ind.lesshs.kappa <- epi.kappa(dat = dd.x.cog.self.ind.lesshs, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
dd.x.cog.self.ind.lesshs.kappa$pabak 
dd.x.cog.self.ind.lesshs.kappa$kappa 
```

```{r}
dd.x.cog.self.ind.lesshs[1,1]*dd.x.cog.self.ind.lesshs[2,2]/(dd.x.cog.self.ind.lesshs[1,2]*dd.x.cog.self.ind.lesshs[2,1])
confusionMatrix(dd.x.cog.self.ind.lesshs)
```

```{r}
dd.x.cog.self.ind.lesshs_wt <- matrix(round(c(dd_cog.self.ind.lesshs_pop[4],dd_cog.self.ind.lesshs_pop[2],dd_cog.self.ind.lesshs_pop[3],dd_cog.self.ind.lesshs_pop[1])), nrow = 2)

dd.x.cog.self.ind.lesshs_wt.kappa <- epi.kappa(dat = dd.x.cog.self.ind.lesshs_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
dd.x.cog.self.ind.lesshs_wt.kappa$pabak 
dd.x.cog.self.ind.lesshs_wt.kappa$kappa 
```

```{r}
dd.x.cog.self.ind.lesshs_wt[1,1]*dd.x.cog.self.ind.lesshs_wt[2,2]/(dd.x.cog.self.ind.lesshs_wt[1,2]*dd.x.cog.self.ind.lesshs_wt[2,1])
confusionMatrix(dd.x.cog.self.ind.lesshs_wt)
```

## DD and Independence Living & Less than HS, prev. and bias adjusted kappa

```{r}
dd.x.ind.lesshs <- table(combined_clean$dd_, combined_clean$ind.lesshs) %>% matrix(nrow = 2) 
dd.x.ind.lesshs <- matrix(c(dd.x.ind.lesshs[2,2],dd.x.ind.lesshs[1,2],dd.x.ind.lesshs[2,1],dd.x.ind.lesshs[1,1]), nrow =2)

dd.x.ind.lesshs.kappa <- epi.kappa(dat = dd.x.ind.lesshs, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
dd.x.ind.lesshs.kappa$pabak 
dd.x.ind.lesshs.kappa$kappa 
```

```{r}
dd.x.ind.lesshs[1,1]*dd.x.ind.lesshs[2,2]/(dd.x.ind.lesshs[1,2]*dd.x.ind.lesshs[2,1])
confusionMatrix(dd.x.ind.lesshs)
```

```{r}
dd.x.ind.lesshs_wt <- matrix(round(c(dd_ind.lesshs_pop[4],dd_ind.lesshs_pop[2],dd_ind.lesshs_pop[3],dd_ind.lesshs_pop[1])), nrow = 2)

dd.x.ind.lesshs_wt.kappa <- epi.kappa(dat = dd.x.ind.lesshs_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
dd.x.ind.lesshs_wt.kappa$pabak 
dd.x.ind.lesshs_wt.kappa$kappa 
```

```{r}
dd.x.ind.lesshs_wt[1,1]*dd.x.ind.lesshs_wt[2,2]/(dd.x.ind.lesshs_wt[1,2]*dd.x.ind.lesshs_wt[2,1])
confusionMatrix(dd.x.ind.lesshs_wt)
```

## DD and (Self-care | Independence Living) & Less than HS, prev. and bias adjusted kappa

```{r}
dd.x.self.ind.lesshs <- table(combined_clean$dd_, combined_clean$self.ind.lesshs) %>% matrix(nrow = 2) 
dd.x.self.ind.lesshs <- matrix(c(dd.x.self.ind.lesshs[2,2],dd.x.self.ind.lesshs[1,2],dd.x.self.ind.lesshs[2,1],dd.x.self.ind.lesshs[1,1]), nrow =2)

dd.x.self.ind.lesshs.kappa <- epi.kappa(dat = dd.x.self.ind.lesshs, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
dd.x.self.ind.lesshs.kappa$pabak 
dd.x.self.ind.lesshs.kappa$kappa 
```

```{r}
dd.x.self.ind.lesshs[1,1]*dd.x.self.ind.lesshs[2,2]/(dd.x.self.ind.lesshs[1,2]*dd.x.self.ind.lesshs[2,1])
confusionMatrix(dd.x.self.ind.lesshs)
```

```{r}
dd.x.self.ind.lesshs_wt <- matrix(round(c(dd_self.ind.lesshs_pop[4],dd_self.ind.lesshs_pop[2],dd_self.ind.lesshs_pop[3],dd_self.ind.lesshs_pop[1])), nrow = 2)

dd.x.self.ind.lesshs_wt.kappa <- epi.kappa(dat = dd.x.self.ind.lesshs_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
dd.x.self.ind.lesshs_wt.kappa$pabak 
dd.x.self.ind.lesshs_wt.kappa$kappa 
```

```{r}
dd.x.self.ind.lesshs_wt[1,1]*dd.x.self.ind.lesshs_wt[2,2]/(dd.x.self.ind.lesshs_wt[1,2]*dd.x.self.ind.lesshs_wt[2,1])
confusionMatrix(dd.x.self.ind.lesshs_wt)
```

## DD and Coginitive & Independence Living & Less than HS, prev. and bias adjusted kappa

```{r}
dd.x.cog.ind.lesshs <- table(combined_clean$dd_, combined_clean$cog.ind.lesshs) %>% matrix(nrow = 2) 
dd.x.cog.ind.lesshs <- matrix(c(dd.x.cog.ind.lesshs[2,2],dd.x.cog.ind.lesshs[1,2],dd.x.cog.ind.lesshs[2,1],dd.x.cog.ind.lesshs[1,1]), nrow =2)

dd.x.cog.ind.lesshs.kappa <- epi.kappa(dat = dd.x.cog.ind.lesshs, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
dd.x.cog.ind.lesshs.kappa$pabak 
dd.x.cog.ind.lesshs.kappa$kappa 
```

```{r}
dd.x.cog.ind.lesshs[1,1]*dd.x.cog.ind.lesshs[2,2]/(dd.x.cog.ind.lesshs[1,2]*dd.x.cog.ind.lesshs[2,1])
confusionMatrix(dd.x.cog.ind.lesshs)
```

```{r}
dd.x.cog.ind.lesshs_wt <- matrix(round(c(dd_cog.ind.lesshs_pop[4],dd_cog.ind.lesshs_pop[2],dd_cog.ind.lesshs_pop[3],dd_cog.ind.lesshs_pop[1])), nrow = 2)

dd.x.cog.ind.lesshs_wt.kappa <- epi.kappa(dat = dd.x.cog.ind.lesshs_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
dd.x.cog.ind.lesshs_wt.kappa$pabak 
dd.x.cog.ind.lesshs_wt.kappa$kappa 
```

```{r}
dd.x.cog.ind.lesshs_wt[1,1]*dd.x.cog.ind.lesshs_wt[2,2]/(dd.x.cog.ind.lesshs_wt[1,2]*dd.x.cog.ind.lesshs_wt[2,1])
confusionMatrix(dd.x.cog.ind.lesshs_wt)
```

## DD and Coginitive & Self-care & Less than HS, prev. and bias adjusted kappa

```{r}
dd.x.cog.self.lesshs <- table(combined_clean$dd_, combined_clean$cog.self.lesshs) %>% matrix(nrow = 2) 
dd.x.cog.self.lesshs <- matrix(c(dd.x.cog.self.lesshs[2,2],dd.x.cog.self.lesshs[1,2],dd.x.cog.self.lesshs[2,1],dd.x.cog.self.lesshs[1,1]), nrow =2)

dd.x.cog.self.lesshs.kappa <- epi.kappa(dat = dd.x.cog.self.lesshs, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
dd.x.cog.self.lesshs.kappa$pabak 
dd.x.cog.self.lesshs.kappa$kappa 
```

```{r}
dd.x.cog.self.lesshs[1,1]*dd.x.cog.self.lesshs[2,2]/(dd.x.cog.self.lesshs[1,2]*dd.x.cog.self.lesshs[2,1])
confusionMatrix(dd.x.cog.self.lesshs)
```

```{r}
dd.x.cog.self.lesshs_wt <- matrix(round(c(dd_cog.self.lesshs_pop[4],dd_cog.self.lesshs_pop[2],dd_cog.self.lesshs_pop[3],dd_cog.self.lesshs_pop[1])), nrow = 2)

dd.x.cog.self.lesshs_wt.kappa <- epi.kappa(dat = dd.x.cog.self.lesshs_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
dd.x.cog.self.lesshs_wt.kappa$pabak 
dd.x.cog.self.lesshs_wt.kappa$kappa 
```

```{r}
dd.x.cog.self.lesshs_wt[1,1]*dd.x.cog.self.lesshs_wt[2,2]/(dd.x.cog.self.lesshs_wt[1,2]*dd.x.cog.self.lesshs_wt[2,1])
confusionMatrix(dd.x.cog.self.lesshs_wt)
```

#############################################################
#############################################################

## IDD and Cog, prev. and bias adjusted kappa

```{r}
idd.x.cog <- table(combined_clean$idd_, combined_clean$cog) %>% matrix(nrow = 2) 
idd.x.cog <- matrix(c(idd.x.cog[2,2],idd.x.cog[1,2],idd.x.cog[2,1],idd.x.cog[1,1]), nrow =2)

idd.x.cog.kappa <- epi.kappa(dat = idd.x.cog, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
idd.x.cog.kappa$pabak 
idd.x.cog.kappa$kappa 
```

```{r}
idd.x.cog[1,1]*idd.x.cog[2,2]/(idd.x.cog[1,2]*idd.x.cog[2,1])
confusionMatrix(idd.x.cog)
```

```{r}
idd.x.cog_wt <- matrix(round(c(idd_cog_pop[4],idd_cog_pop[2],idd_cog_pop[3],idd_cog_pop[1])), nrow = 2)

idd.x.cog_wt.kappa <- epi.kappa(dat = idd.x.cog_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
idd.x.cog_wt.kappa$pabak 
idd.x.cog_wt.kappa$kappa 
```

```{r}
idd.x.cog_wt[1,1]*idd.x.cog_wt[2,2]/(idd.x.cog_wt[1,2]*idd.x.cog_wt[2,1])
confusionMatrix(idd.x.cog_wt)
```

## IDD and Cog & Self-care, prev. and bias adjusted kappa

```{r}
idd.x.cog.self <- table(combined_clean$idd_, combined_clean$cog.self) %>% matrix(nrow = 2) 
idd.x.cog.self <- matrix(c(idd.x.cog.self[2,2],idd.x.cog.self[1,2],idd.x.cog.self[2,1],idd.x.cog.self[1,1]), nrow =2)

idd.x.cog.self.kappa <- epi.kappa(dat = idd.x.cog.self, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
idd.x.cog.self.kappa$pabak 
idd.x.cog.self.kappa$kappa 
```

```{r}
idd.x.cog.self[1,1]*idd.x.cog.self[2,2]/(idd.x.cog.self[1,2]*idd.x.cog.self[2,1])
confusionMatrix(idd.x.cog.self)
```

```{r}
idd.x.cog.self_wt <- matrix(round(c(idd_cog.self_pop[4],idd_cog.self_pop[2],idd_cog.self_pop[3],idd_cog.self_pop[1])), nrow = 2)

idd.x.cog.self_wt.kappa <- epi.kappa(dat = idd.x.cog.self_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
idd.x.cog.self_wt.kappa$pabak 
idd.x.cog.self_wt.kappa$kappa 
```

```{r}
idd.x.cog.self_wt[1,1]*idd.x.cog.self_wt[2,2]/(idd.x.cog.self_wt[1,2]*idd.x.cog.self_wt[2,1])
confusionMatrix(idd.x.cog.self_wt)
```

## IDD and Cog & Independent Living, prev. and bias adjusted kappa

```{r}
idd.x.cog.ind <- table(combined_clean$idd_, combined_clean$cog.ind) %>% matrix(nrow = 2) 
idd.x.cog.ind <- matrix(c(idd.x.cog.ind[2,2],idd.x.cog.ind[1,2],idd.x.cog.ind[2,1],idd.x.cog.ind[1,1]), nrow =2)

idd.x.cog.ind.kappa <- epi.kappa(dat = idd.x.cog.ind, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
idd.x.cog.ind.kappa$pabak 
idd.x.cog.ind.kappa$kappa 
```

```{r}
idd.x.cog.ind[1,1]*idd.x.cog.ind[2,2]/(idd.x.cog.ind[1,2]*idd.x.cog.ind[2,1])
confusionMatrix(idd.x.cog.ind)
```

```{r}
idd.x.cog.ind_wt <- matrix(round(c(idd_cog.ind_pop[4],idd_cog.ind_pop[2],idd_cog.ind_pop[3],idd_cog.ind_pop[1])), nrow = 2)

idd.x.cog.ind_wt.kappa <- epi.kappa(dat = idd.x.cog.ind_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
idd.x.cog.ind_wt.kappa$pabak 
idd.x.cog.ind_wt.kappa$kappa 
```

```{r}
idd.x.cog.ind_wt[1,1]*idd.x.cog.ind_wt[2,2]/(idd.x.cog.ind_wt[1,2]*idd.x.cog.ind_wt[2,1])
confusionMatrix(idd.x.cog.ind_wt)
```

## IDD and Cog & (Self-care | Independent Living), prev. and bias adjusted kappa

```{r}
idd.x.cog.self.ind <- table(combined_clean$idd_, combined_clean$cog.self.ind) %>% matrix(nrow = 2) 
idd.x.cog.self.ind <- matrix(c(idd.x.cog.self.ind[2,2],idd.x.cog.self.ind[1,2],idd.x.cog.self.ind[2,1],idd.x.cog.self.ind[1,1]), nrow =2)

idd.x.cog.self.ind.kappa <- epi.kappa(dat = idd.x.cog.self.ind, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
idd.x.cog.self.ind.kappa$pabak 
idd.x.cog.self.ind.kappa$kappa 
```

```{r}
idd.x.cog.self.ind[1,1]*idd.x.cog.self.ind[2,2]/(idd.x.cog.self.ind[1,2]*idd.x.cog.self.ind[2,1])
confusionMatrix(idd.x.cog.self.ind)
```

```{r}
idd.x.cog.self.ind_wt <- matrix(round(c(idd_cog.self.ind_pop[4],idd_cog.self.ind_pop[2],idd_cog.self.ind_pop[3],idd_cog.self.ind_pop[1])), nrow = 2)

idd.x.cog.self.ind_wt.kappa <- epi.kappa(dat = idd.x.cog.self.ind_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
idd.x.cog.self.ind_wt.kappa$pabak 
idd.x.cog.self.ind_wt.kappa$kappa 
```

```{r}
idd.x.cog.self.ind_wt[1,1]*idd.x.cog.self.ind_wt[2,2]/(idd.x.cog.self.ind_wt[1,2]*idd.x.cog.self.ind_wt[2,1])
confusionMatrix(idd.x.cog.self.ind_wt)
```

## IDD and Independent Living & Less than HS, prev. and bias adjusted kappa

```{r}
idd.x.ind.lesshs <- table(combined_clean$idd_, combined_clean$ind.lesshs) %>% matrix(nrow = 2) 
idd.x.ind.lesshs <- matrix(c(idd.x.ind.lesshs[2,2],idd.x.ind.lesshs[1,2],idd.x.ind.lesshs[2,1],idd.x.ind.lesshs[1,1]), nrow =2)

idd.x.ind.lesshs.kappa <- epi.kappa(dat = idd.x.ind.lesshs, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
idd.x.ind.lesshs.kappa$pabak 
idd.x.ind.lesshs.kappa$kappa 
```

```{r}
idd.x.ind.lesshs[1,1]*idd.x.ind.lesshs[2,2]/(idd.x.ind.lesshs[1,2]*idd.x.ind.lesshs[2,1])
confusionMatrix(idd.x.ind.lesshs)
```

```{r}
idd.x.ind.lesshs_wt <- matrix(round(c(idd_ind.lesshs_pop[4],idd_ind.lesshs_pop[2],idd_ind.lesshs_pop[3],idd_ind.lesshs_pop[1])), nrow = 2)

idd.x.ind.lesshs_wt.kappa <- epi.kappa(dat = idd.x.ind.lesshs_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
idd.x.ind.lesshs_wt.kappa$pabak 
idd.x.ind.lesshs_wt.kappa$kappa 
```

```{r}
idd.x.ind.lesshs_wt[1,1]*idd.x.ind.lesshs_wt[2,2]/(idd.x.ind.lesshs_wt[1,2]*idd.x.ind.lesshs_wt[2,1])
confusionMatrix(idd.x.ind.lesshs_wt)
```

## IDD and (Self-care | Independent Living) & Less than HS, prev. and bias adjusted kappa

```{r}
idd.x.self.ind.lesshs <- table(combined_clean$idd_, combined_clean$self.ind.lesshs) %>% matrix(nrow = 2) 
idd.x.self.ind.lesshs <- matrix(c(idd.x.self.ind.lesshs[2,2],idd.x.self.ind.lesshs[1,2],idd.x.self.ind.lesshs[2,1],idd.x.self.ind.lesshs[1,1]), nrow =2)

idd.x.self.ind.lesshs.kappa <- epi.kappa(dat = idd.x.self.ind.lesshs, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
idd.x.self.ind.lesshs.kappa$pabak 
idd.x.self.ind.lesshs.kappa$kappa 
```

```{r}
idd.x.self.ind.lesshs[1,1]*idd.x.self.ind.lesshs[2,2]/(idd.x.self.ind.lesshs[1,2]*idd.x.self.ind.lesshs[2,1])
confusionMatrix(idd.x.self.ind.lesshs)
```

```{r}
idd.x.self.ind.lesshs_wt <- matrix(round(c(idd_self.ind.lesshs_pop[4],idd_self.ind.lesshs_pop[2],idd_self.ind.lesshs_pop[3],idd_self.ind.lesshs_pop[1])), nrow = 2)

idd.x.self.ind.lesshs_wt.kappa <- epi.kappa(dat = idd.x.self.ind.lesshs_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
idd.x.self.ind.lesshs_wt.kappa$pabak 
idd.x.self.ind.lesshs_wt.kappa$kappa 
```

```{r}
idd.x.self.ind.lesshs_wt[1,1]*idd.x.self.ind.lesshs_wt[2,2]/(idd.x.self.ind.lesshs_wt[1,2]*idd.x.self.ind.lesshs_wt[2,1])
confusionMatrix(idd.x.self.ind.lesshs_wt)
```

## IDD and Cognitive Independent Living & Less than HS, prev. and bias adjusted kappa

```{r}
idd.x.cog.ind.lesshs <- table(combined_clean$idd_, combined_clean$cog.ind.lesshs) %>% matrix(nrow = 2) 
idd.x.cog.ind.lesshs <- matrix(c(idd.x.cog.ind.lesshs[2,2],idd.x.cog.ind.lesshs[1,2],idd.x.cog.ind.lesshs[2,1],idd.x.cog.ind.lesshs[1,1]), nrow =2)

idd.x.cog.ind.lesshs.kappa <- epi.kappa(dat = idd.x.cog.ind.lesshs, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
idd.x.cog.ind.lesshs.kappa$pabak 
idd.x.cog.ind.lesshs.kappa$kappa 
```

```{r}
idd.x.cog.ind.lesshs[1,1]*idd.x.cog.ind.lesshs[2,2]/(idd.x.cog.ind.lesshs[1,2]*idd.x.cog.ind.lesshs[2,1])
confusionMatrix(idd.x.cog.ind.lesshs)
```

```{r}
idd.x.cog.ind.lesshs_wt <- matrix(round(c(idd_cog.ind.lesshs_pop[4],idd_cog.ind.lesshs_pop[2],idd_cog.ind.lesshs_pop[3],idd_cog.ind.lesshs_pop[1])), nrow = 2)

idd.x.cog.ind.lesshs_wt.kappa <- epi.kappa(dat = idd.x.cog.ind.lesshs_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
idd.x.cog.ind.lesshs_wt.kappa$pabak 
idd.x.cog.ind.lesshs_wt.kappa$kappa 
```

```{r}
idd.x.cog.ind.lesshs_wt[1,1]*idd.x.cog.ind.lesshs_wt[2,2]/(idd.x.cog.ind.lesshs_wt[1,2]*idd.x.cog.ind.lesshs_wt[2,1])
confusionMatrix(idd.x.cog.ind.lesshs_wt)
```

## IDD and Cognitive Self-care & Less than HS, prev. and bias adjusted kappa

```{r}
idd.x.cog.self.lesshs <- table(combined_clean$idd_, combined_clean$cog.self.lesshs) %>% matrix(nrow = 2) 
idd.x.cog.self.lesshs <- matrix(c(idd.x.cog.self.lesshs[2,2],idd.x.cog.self.lesshs[1,2],idd.x.cog.self.lesshs[2,1],idd.x.cog.self.lesshs[1,1]), nrow =2)

idd.x.cog.self.lesshs.kappa <- epi.kappa(dat = idd.x.cog.self.lesshs, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
idd.x.cog.self.lesshs.kappa$pabak 
idd.x.cog.self.lesshs.kappa$kappa 
```

```{r}
idd.x.cog.self.lesshs[1,1]*idd.x.cog.self.lesshs[2,2]/(idd.x.cog.self.lesshs[1,2]*idd.x.cog.self.lesshs[2,1])
confusionMatrix(idd.x.cog.self.lesshs)
```

```{r}
idd.x.cog.self.lesshs_wt <- matrix(round(c(idd_cog.self.lesshs_pop[4],idd_cog.self.lesshs_pop[2],idd_cog.self.lesshs_pop[3],idd_cog.self.lesshs_pop[1])), nrow = 2)

idd.x.cog.self.lesshs_wt.kappa <- epi.kappa(dat = idd.x.cog.self.lesshs_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
idd.x.cog.self.lesshs_wt.kappa$pabak 
idd.x.cog.self.lesshs_wt.kappa$kappa 
```

```{r}
idd.x.cog.self.lesshs_wt[1,1]*idd.x.cog.self.lesshs_wt[2,2]/(idd.x.cog.self.lesshs_wt[1,2]*idd.x.cog.self.lesshs_wt[2,1])
confusionMatrix(idd.x.cog.self.lesshs_wt)
```

## IDD and Cognitive & (Independent Living | Self-care) & Less than HS, prev. and bias adjusted kappa

```{r}
idd.x.cog.self.ind.lesshs <- table(combined_clean$idd_, combined_clean$cog.self.ind.lesshs) %>% matrix(nrow = 2) 
idd.x.cog.self.ind.lesshs <- matrix(c(idd.x.cog.self.ind.lesshs[2,2],idd.x.cog.self.ind.lesshs[1,2],idd.x.cog.self.ind.lesshs[2,1],idd.x.cog.self.ind.lesshs[1,1]), nrow =2)

idd.x.cog.self.ind.lesshs.kappa <- epi.kappa(dat = idd.x.cog.self.ind.lesshs, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
idd.x.cog.self.ind.lesshs.kappa$pabak 
idd.x.cog.self.ind.lesshs.kappa$kappa 
```

```{r}
idd.x.cog.self.ind.lesshs[1,1]*idd.x.cog.self.ind.lesshs[2,2]/(idd.x.cog.self.ind.lesshs[1,2]*idd.x.cog.self.ind.lesshs[2,1])
confusionMatrix(idd.x.cog.self.ind.lesshs)
```

```{r}
idd.x.cog.self.ind.lesshs_wt <- matrix(round(c(idd_cog.self.ind.lesshs_pop[4],idd_cog.self.ind.lesshs_pop[2],idd_cog.self.ind.lesshs_pop[3],idd_cog.self.ind.lesshs_pop[1])), nrow = 2)

idd.x.cog.self.ind.lesshs_wt.kappa <- epi.kappa(dat = idd.x.cog.self.ind.lesshs_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
idd.x.cog.self.ind.lesshs_wt.kappa$pabak 
idd.x.cog.self.ind.lesshs_wt.kappa$kappa 
```

```{r}
idd.x.cog.self.ind.lesshs_wt[1,1]*idd.x.cog.self.ind.lesshs_wt[2,2]/(idd.x.cog.self.ind.lesshs_wt[1,2]*idd.x.cog.self.ind.lesshs_wt[2,1])
confusionMatrix(idd.x.cog.self.ind.lesshs_wt)
```

# ID model

```{r}
svydes_proxy

id_mod <- svyglm(id_ ~ cog + ind + lesshs + 
                cog*ind + cog*lesshs + ind*lesshs + cog*ind*lesshs,
              family = quasibinomial,
              design = svydes_proxy)
summary(id_mod)
tidy(id_mod, expo=TRUE, conf.int=TRUE)

set.seed(0)
id_pred_df <- data.frame(
  dat = combined_clean %>% select(id_,cog,ind,lesshs,PSU,STRAT,WTFA_AFD),
  id_mod_pred = predict(id_mod, type = "response", se = TRUE),
  rnrml = rnorm(dim(combined_clean)[1]))

id_pred_df <- id_pred_df %>% 
  mutate(jitter = id_mod_pred.response + rnrml*id_mod_pred.SE)

id_prop[2] # target
id_roc <- roc(id_pred_df$dat.id_,id_pred_df$id_mod_pred.response)
plot.roc(id_pred_df$dat.id_,id_pred_df$id_mod_pred.response)


eps <- Inf
cutoff <- sum(id_pred_df$dat.id_)/dim(combined_clean)[1] #unweighted prop
prev_cutoff = 1

while (eps > 1e-5){
  id_pred_df <- id_pred_df %>%
    mutate(new_pred = ifelse(jitter > cutoff, 1, 0))
  svydes_mod <- survey::svydesign(ids = ~dat.PSU,
                            data = id_pred_df,
                            strata = ~dat.STRAT,
                            weights = ~dat.WTFA_AFD,
                            nest = T)
  prop_est <- svymean(~new_pred,svydes_mod)[1]
  cutoff <- cutoff + cutoff*(prop_est-id_prop[2])/(prev_cutoff)
  eps = abs(prop_est - id_prop[2])
  print(eps)
  prev_cutoff <- cutoff
}

table(id_pred_df$dat.id_,id_pred_df$new_pred)

id_table <- svyby(~new_pred, by = ~dat.cog + dat.ind + dat.lesshs, design = svydes_mod, svymean)
```


## ID MODEL EVAL

```{r}
id.x.mod <- table(id_pred_df$dat.id_, id_pred_df$new_pred) %>% matrix(nrow = 2) 
id.x.mod <- matrix(c(id.x.mod[2,2],id.x.mod[1,2],id.x.mod[2,1],id.x.mod[1,1]), nrow =2)

id.x.mod.kappa <- epi.kappa(dat = id.x.mod, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
id.x.mod.kappa$pabak 
id.x.mod.kappa$kappa 
```

```{r}
id.x.mod[1,1]*id.x.mod[2,2]/(id.x.mod[1,2]*id.x.mod[2,1])
confusionMatrix(id.x.mod)
```

```{r}
table(id_pred_df$dat.id_, id_pred_df$new_pred)
id_pred_df <- id_pred_df %>%
  mutate(id.x.new_pred = paste0(dat.id_,new_pred))

svydes_mod <- survey::svydesign(ids = ~dat.PSU,
                            data = id_pred_df,
                            strata = ~dat.STRAT,
                            weights = ~dat.WTFA_AFD,
                            nest = T)

id.x.new_pred_pop  <- svytotal(~id.x.new_pred, design = svydes_mod)
id.x.new_pred_prev <- svymean(~id.x.new_pred, design = svydes_mod)
```

```{r}
id.x.new_pred_wt <- matrix(round(c(id.x.new_pred_pop[4],id.x.new_pred_pop[2],id.x.new_pred_pop[3],id.x.new_pred_pop[1])), nrow = 2)

id.x.new_pred_wt.kappa <- epi.kappa(dat = id.x.new_pred_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
id.x.new_pred_wt.kappa$pabak 
id.x.new_pred_wt.kappa$kappa 
```

```{r}
id.x.new_pred_wt[1,1]*id.x.new_pred_wt[2,2]/(id.x.new_pred_wt[1,2]*id.x.new_pred_wt[2,1])
confusionMatrix(id.x.new_pred_wt)
```

# DD model

```{r}
dd_mod <- svyglm(dd_ ~ cog + self + lesshs + 
                cog*self + cog*lesshs + self*lesshs + cog*self*lesshs,
              family = quasibinomial,
              design = svydes_proxy)
summary(dd_mod)
tidy(dd_mod, expo=TRUE, conf.int=TRUE)

set.seed(0)
dd_pred_df <- data.frame(
  dat = combined_clean %>% select(dd_,cog,self,lesshs,PSU,STRAT,WTFA_AFD),
  dd_mod_pred = predict(dd_mod, type = "response", se = TRUE),
  rnrml = rnorm(dim(combined_clean)[1]))

dd_pred_df <- dd_pred_df %>% 
  mutate(jitter = dd_mod_pred.response + rnrml*dd_mod_pred.SE)

dd_prop[2] # target
dd_roc <- roc(dd_pred_df$dat.dd_,dd_pred_df$dd_mod_pred.response)
plot.roc(dd_pred_df$dat.dd_,dd_pred_df$dd_mod_pred.response)


eps <- Inf
cutoff <- sum(dd_pred_df$dat.dd_)/dim(combined_clean)[1] #unweighted prop
prev_cutoff = 1

while (eps > 1e-5){
  dd_pred_df <- dd_pred_df %>%
    mutate(new_pred = ifelse(jitter > cutoff, 1, 0))
  svydes_mod <- survey::svydesign(ids = ~dat.PSU,
                            data = dd_pred_df,
                            strata = ~dat.STRAT,
                            weights = ~dat.WTFA_AFD,
                            nest = T)
  prop_est <- svymean(~new_pred,svydes_mod)[1]
  cutoff <- cutoff + cutoff*(prop_est-dd_prop[2])/(prev_cutoff)
  eps = abs(prop_est - dd_prop[2])
  print(eps)
  prev_cutoff <- cutoff
}

table(dd_pred_df$dat.dd_,dd_pred_df$new_pred)

dd_table <- svyby(~new_pred, by = ~dat.cog + dat.self + dat.lesshs, design = svydes_mod, svymean)
dd_table
```

## DD MODEL EVAL

```{r}
dd.x.mod <- table(dd_pred_df$dat.dd_, dd_pred_df$new_pred) %>% matrix(nrow = 2) 
dd.x.mod <- matrix(c(dd.x.mod[2,2],dd.x.mod[1,2],dd.x.mod[2,1],dd.x.mod[1,1]), nrow =2)

dd.x.mod.kappa <- epi.kappa(dat = dd.x.mod, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
dd.x.mod.kappa$pabak 
dd.x.mod.kappa$kappa 
```

```{r}
dd.x.mod[1,1]*dd.x.mod[2,2]/(dd.x.mod[1,2]*dd.x.mod[2,1])
confusionMatrix(dd.x.mod)
```

```{r}
table(dd_pred_df$dat.dd_, dd_pred_df$new_pred)
dd_pred_df <- dd_pred_df %>%
  mutate(dd.x.new_pred = paste0(dat.dd_,new_pred))

svydes_mod <- survey::svydesign(ids = ~dat.PSU,
                            data = dd_pred_df,
                            strata = ~dat.STRAT,
                            weights = ~dat.WTFA_AFD,
                            nest = T)

dd.x.new_pred_pop  <- svytotal(~dd.x.new_pred, design = svydes_mod)
dd.x.new_pred_prev <- svymean(~dd.x.new_pred, design = svydes_mod)
```

```{r}
dd.x.new_pred_wt <- matrix(round(c(dd.x.new_pred_pop[4],dd.x.new_pred_pop[2],dd.x.new_pred_pop[3],dd.x.new_pred_pop[1])), nrow = 2)

dd.x.new_pred_wt.kappa <- epi.kappa(dat = dd.x.new_pred_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
dd.x.new_pred_wt.kappa$pabak 
dd.x.new_pred_wt.kappa$kappa 
```

```{r}
dd.x.new_pred_wt[1,1]*dd.x.new_pred_wt[2,2]/(dd.x.new_pred_wt[1,2]*dd.x.new_pred_wt[2,1])
confusionMatrix(dd.x.new_pred_wt)
```

# IDD model

```{r}
idd_mod <- svyglm(idd_ ~ cog + ind + lesshs + 
                cog*ind + cog*lesshs + ind*lesshs + cog*ind*lesshs,
              family = quasibinomial,
              design = svydes_proxy)
summary(idd_mod)
tidy(idd_mod, expo=TRUE, conf.int=TRUE)

set.seed(0)
idd_pred_df <- data.frame(
  dat = combined_clean %>% select(idd_,cog,ind,lesshs,PSU,STRAT,WTFA_AFD),
  idd_mod_pred = predict(idd_mod, type = "response", se = TRUE),
  rnrml = rnorm(dim(combined_clean)[1]))

idd_pred_df <- idd_pred_df %>% 
  mutate(jitter = idd_mod_pred.response + rnrml*idd_mod_pred.SE)

idd_prop[2] # target
idd_roc <- roc(idd_pred_df$dat.idd_,idd_pred_df$idd_mod_pred.response)
plot.roc(idd_pred_df$dat.idd_,idd_pred_df$idd_mod_pred.response)


eps <- Inf
cutoff <- sum(idd_pred_df$dat.idd_)/dim(combined_clean)[1] #unweighted prop
prev_cutoff = 1

while (eps > 1e-5){
  idd_pred_df <- idd_pred_df %>%
    mutate(new_pred = ifelse(jitter > cutoff, 1, 0))
  svydes_mod <- survey::svydesign(ids = ~dat.PSU,
                            data = idd_pred_df,
                            strata = ~dat.STRAT,
                            weights = ~dat.WTFA_AFD,
                            nest = T)
  prop_est <- svymean(~new_pred,svydes_mod)[1]
  cutoff <- cutoff + cutoff*(prop_est-idd_prop[2])/(prev_cutoff)
  eps = abs(prop_est - idd_prop[2])
  print(eps)
  prev_cutoff <- cutoff
}

table(idd_pred_df$dat.idd_,idd_pred_df$new_pred)

idd_table <- svyby(~new_pred, by = ~dat.cog + dat.ind + dat.lesshs, design = svydes_mod, svymean)
```

## IDD MODEL EVAL

```{r}
idd.x.mod <- table(idd_pred_df$dat.idd_, idd_pred_df$new_pred) %>% matrix(nrow = 2) 
idd.x.mod <- matrix(c(idd.x.mod[2,2],idd.x.mod[1,2],idd.x.mod[2,1],idd.x.mod[1,1]), nrow =2)

idd.x.mod.kappa <- epi.kappa(dat = idd.x.mod, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
idd.x.mod.kappa$pabak 
idd.x.mod.kappa$kappa 
```

```{r}
idd.x.mod[1,1]*idd.x.mod[2,2]/(idd.x.mod[1,2]*idd.x.mod[2,1])
confusionMatrix(idd.x.mod)
```

```{r}
table(idd_pred_df$dat.idd_, idd_pred_df$new_pred)
idd_pred_df <- idd_pred_df %>%
  mutate(idd.x.new_pred = paste0(dat.idd_,new_pred))

svydes_mod <- survey::svydesign(ids = ~dat.PSU,
                            data = idd_pred_df,
                            strata = ~dat.STRAT,
                            weights = ~dat.WTFA_AFD,
                            nest = T)

idd.x.new_pred_pop  <- svytotal(~idd.x.new_pred, design = svydes_mod)
idd.x.new_pred_prev <- svymean(~idd.x.new_pred, design = svydes_mod)
```

```{r}
idd.x.new_pred_wt <- matrix(round(c(idd.x.new_pred_pop[4],idd.x.new_pred_pop[2],idd.x.new_pred_pop[3],idd.x.new_pred_pop[1])), nrow = 2)

idd.x.new_pred_wt.kappa <- epi.kappa(dat = idd.x.new_pred_wt, method = "fleiss", alternative = "two.sided", conf.level = 0.95)
idd.x.new_pred_wt.kappa$pabak 
idd.x.new_pred_wt.kappa$kappa 
```

```{r}
idd.x.new_pred_wt[1,1]*idd.x.new_pred_wt[2,2]/(idd.x.new_pred_wt[1,2]*idd.x.new_pred_wt[2,1])
confusionMatrix(idd.x.new_pred_wt)
```






